Protected Areas Practical

### 2024-11-25 tutorial/MSc_PA_practical_answers.Rmd
small edits

- Learn how and why protected areas are important
- Learn how to implement a protected area network

@@

```r
# if needed, install HiGHS solver, but this should have been done before the practical
install.packages("highs", repos = "https://cran.rstudio.com/")
```

>>>>

- Learn how and why protected areas are important (Lecture)
- Lear the principles of systematic conservation planning (Lecture)
- Learn how to implement a protected area network (Lecture + Practical)

@@

```r
# test the installation
library(highs)

# if needed, install HiGHS solver, but this should have been done before the practical
install.packages("highs", repos = "https://cran.rstudio.com/")
```
